Comparison of two object-oriented languages: Eiffel and Ruby

### 2014-01-13 paper.tex
commit last changes

\usepackage{natbib}

% Listing settings
\lstset{language=Ruby,
        basicstyle=\scriptsize,
        backgroundcolor=\color{Gray},
        commentstyle=\color{White},
        numberstyle=\scriptsize\color{Black},
        morekeywords={puts, private, public, protected},
        keywordstyle=\color{Blue},
        numbers=left,
        xleftmargin=9pt,
        framexleftmargin=9pt,
        breaklines=true,
        numbersep=1pt,
        tabsize=2}

@@

Every value in both Eiffel and Ruby are object, even types that are in many languages called primitive types (for example: integers, booleans). Eiffel and Ruby have a similar structure. There is in both languages a class at the top of the hierarchy, this means a class from which every other class in the language inherits its methods. In Ruby this class is called BasicObject\cite{basicObjectDoc} and in Eiffel it is called ANY\cite{meyer2001eiffel}. Besides the ANY class, Eiffel also has the NONE class, which is the class that inherits from every class in the language. Ruby pushes the object-orientation a little bit further with meta-classes. This subject will come back later on in section \ref{sec:metaclass}.

@@

\subsubsection{Metaclass model}

@@

% http://en.wikipedia.org/wiki/Metaclass
A metaclass is a special class that has classes as instances. It defines thus methods that every class and its instances should have. When asking to a class in Ruby from which class it is an instance, it will always return the class Class. This is logical since every class should inherit the methods defined in it. Thus the only metaclass in Ruby is thus the class Class.

@@

\caption{The Ruby metaclass model. Image from Wikipedia}

>>>>

\usepackage{natbib}
\renewcommand{\bibsection}{}

% Listing settings
\lstset{language=Ruby,
        basicstyle=\scriptsize,
        backgroundcolor=\color{White},
        commentstyle=\color{Gray},
        numberstyle=\scriptsize\color{Black},
        morekeywords={puts, private, public, protected},
        keywordstyle=\color{Blue},
        numbers=left,
        xleftmargin=9pt,
        framexleftmargin=9pt,
        breaklines=true,
        numbersep=1pt,
        tabsize=2}

@@

Every value in both Eiffel and Ruby are object, even types that are in many languages called primitive types (for example: integers, booleans). Eiffel and Ruby have a similar structure. There is in both languages a class at the top of the hierarchy, this means a class from which every other class in the language inherits its methods. In Ruby this class is called BasicObject\cite{basicObjectDoc} and in Eiffel it is called ANY\cite{meyer2001eiffel}. Besides the ANY class, Eiffel also has the NONE class, which is the class that inherits from every class in the language. Ruby pushes the object-orientation a little bit further with meta-objects. This subject will come back later on in section \ref{sec:metaclass}.

@@

\subsubsection{Metamodel}

@@

A metaclass \cite{wiki:metaclass, rubyMetaclass} is a special class that has classes as instances. It defines thus methods that every class and its instances should have. When asking to a class in Ruby from which class it is an instance, it will always return the class Class. This is logical since every class should inherit the methods defined in it. Thus the only metaclass in Ruby is thus the class Class.

@@

\caption{The Ruby metaclass model. Image from Wikipedia \cite{wiki:metaclass}}
